My title

### 2024-11-04 paper/paper.qmd
data, appendices, citations

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

@@

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

@@

The aggregated polling data includes support percentages of different presidential candidates in polls with different FiveThirtyEight ratings [CITATION HERE https://abcnews.go.com/538/best-pollsters-america/story?id=105563951] across two elections. Please view [UPDATE APPENDIX] for summary statistics of sub-datasets.

@@

@@

```
\FloatBarrier

### Sponsored

@@

@@

@@

@@

# Appendix {-}
## Pollster methodology overview and evaluation
The Quinnipiac University Poll conducts independent polling in swing states - to analyze their methodology, we look specifically into their October 2024 Pennsylvania polls.

Their target population is likely voters aged 18 and older in Pennsylvania. To reach this population, they use likely voters aged 18 and older with phone numbers (both landline and cell) as their sampling frame, i.e. the frame of possible subjects that they sample observations from. Quinnipiac University employed Random Digit Dialing (RDD) to generate their sample of 2,186 respondents. This dual-frame approach reflects modern communication patterns, with 1,644 cell phone and 542 landline completions. However, using phones as a sampling frame means they cannot reach voters without phone access, introducing potential coverage bias.

Their sampling approach uses stratification by Census division according to area code, meaning that they divide Pennsylvania into geographic regions before using RDD to sample within each region. This strategy ensures even geographic representation but adds complexity to the sampling process. For each selected number, they attempt contact at least three times before marking it as non-responsive. For landline calls, they ask to speak with the household member who has the next birthday, a simple but effective randomization technique. Afterwards, a series of screening questions confirm that the subject is indeed a likely voter, after which the subject's responses are then formally taken as part of the sample.

After collecting responses, Quinnipiac adjusts their data through post-stratification weighting. In this weighting, they compare their sample's demographic composition to known population benchmarks from the Census (like age, gender, education, and race distributions in Pennsylvania) and adjust the weight given to each response to match these benchmarks. For example, if their sample has too few young voters compared to Census data, responses from young voters would be weighted more heavily. While this helps correct for sampling imbalances, it can increase the variance in their estimates if the weights vary substantially.

The survey administration addresses measurement issues through its design. Live interviewers conduct all interviews, enabling question clarification and generating higher response rates compared to automated systems. However, live interviewers may introduce social desirability bias, where respondents might modify their answers to appear more socially acceptable. This becomes particularly relevant in political polling, where respondents might hesitate to express unpopular political views.

Several types of bias affect the poll's results. Self-selection bias occurs because certain types of people (typically those more politically engaged or with stronger views) are more likely to agree to participate in the survey. Non-response bias arises when people who respond differ systematically from those who don't - for instance, busier people might be less likely to answer calls, potentially underrepresenting certain occupational groups. Coverage bias means some groups (like those without phones) have no chance of being included in the sample.

@@

Overall, Quinnipiac's methodology represents a balanced approach to managing practical constraints and statistical rigor in modern political polling - while some common biases are still likely to skew the poll results off the true support levels for Harris, for example, the poll uses methods such as post-stratification weighting to tradeoff biases at the cost of model variance. Using live interviewers unavoidably introduces social desirability bias, however, and significantly increases poll costs per quota. Modifying the methodology to remove this aspect of the survey would potentially reduce bias and allow for larger samples to be taken, in turn opening up possibilities for cross-validation and the such, which then reduces the effect of increased model variance on the final results.

@@

Our sampling strategy employs both probability and non-probability methods. Probability sampling (60% of budget, i.e. $60k) means every member of our target population has a known, non-zero chance of being selected - this allows us to calculate proper margins of error and make statistical inferences about the population. For this, we use dual-frame random digit dialing (RDD) for phone surveys and address-based sampling (ABS) for mail-to-web recruitment. RDD involves generating random phone numbers within active area codes, while ABS uses the U.S. Postal Service's delivery database as a sampling frame. The ABS approach helps reach households without reliable phone access. We stratify our sample by geography, demographics, and previous voting patterns to ensure representation across key subgroups - meaning we divide the population into these subgroups and sample from each independently.

For non-probability sampling (40% of budget, i.e. $40k), where respondents' selection probabilities are unknown and not everyone has a chance of being selected, we recruit through multiple online panel vendors and use targeted social media advertising to reach traditionally underrepresented groups. While this approach introduces potential selection bias because participants self-select into the sample, it helps reach younger voters who are less responsive to traditional survey methods. We implement quota sampling within these non-probability samples to match key demographic targets - for example, stopping collection from certain demographic groups once their quota is filled.

@@

Our weighting approach uses post-stratification to known population benchmarks - this means we adjust the weight given to each response so that our sample matches known population characteristics. For example, if our sample has 30% college graduates but the population has 40%, we would give more weight to responses from college graduates. We include demographics (age, race, education, gender), geographic location, past voting behavior, and party registration in our weighting scheme. We produce daily estimates using a 7-day rolling average, which helps smooth out daily fluctuations while remaining responsive to real changes in voter preferences.

Finally, how ethics are handled is a crucial part of any survey methodology. In this idealised methodology, consent will be asked for at the beginning of the survey, full disclosure of how information is used will be given beforehand and no self-identifiable information will be recorded (so no names, phone numbers, etc.). The $10 incentive is enough to hopefully make it worthwile for participants' time, but also not ideally not significant enough of an incentive to make individuals suppress otherwise deal-breaking concerns with the survey purely for the sake of the incentive.

>>>>

We use the statistical programming language R [@R] for the graphing, analysis and presentation of the project as a whole. Caret [@caret], glmnet [@glmnet; @glmnet2; @glmnet3], nnet [@nnet], lubridate [@lubridate] and pROC [@pROC] were used directly in the analysis of the data. Tidyverse [@tidyverse], stringr [@stringr], dplyr [@dplyr], and styler [@styler] were used in the presentation and/or styling of the data, graphs, and paper as a whole.

In order to build a model that predicts the results of the 2024 election, we use survey/poll data on likely voters to inform our insights regarding likely election results, an approach widely accepted in political contexts [@politicalpolling]. We use a poll-of-polls dataset from 538 [@538data], consisting of aggregated polling data from FiveThirtyEight's 2024 presidential election polling database from various national and state-level polls from pollsters all around the country, recording information such as the date when the poll concluded, the entity conducting the poll, and the estimated support rate of the candidate as given by the poll. The data spans national and state-level polls, with particular focus on key battleground states that could determine the Electoral College outcome. This dataset was chosen over alternatives like RealClearPolitics because of 538's comprehensive methodological adjustments and transparent quality standards for included polls.

After cleaning the data to split results by candidate, remove polls with N/A values and ratings lower than 2.5, and further selecting polls polling likely voters as opposed to the whole population, we are left with 746 data points with the variables pollster, has_sponsor, numeric_grade, pollscore, transparency_score, sample_size, end_date, state, candidate_name, pct (support rate in percentage), and cycle (election cycle, i.e. 2020/2024).

@@

The "from-voter-to-data" process for the 538 dataset involves three processes: measurement, where voter responses are collected and adjusted to best provide insight into a true support percentage population parameter, data collection, where data from polls is obtained and cleaned by 538 to only include polls adhering to their set of standards, and aggregation, where additional scores/variables are given to each poll to reflect their accuracy, transparency and bias levels with regards to polling scores [@5381; @5382; @5383].

The measurement process involves several sequential steps, beginning with initial data collection where pollsters conduct surveys using various modes such as phone, online, or mixed-mode approaches to gather voter preferences. Sample processing follows, involving likely voter screens to identify probable voters, demographic weighting to match population benchmarks, and various adjustments to ensure representativeness.

The data collection process involves obtaining data from various election polls from around the country, given that they meet specific methodological criteria. Each included poll must provide clear documentation of pollster identity, survey dates, and sampled population, maintain a minimum sample size of 100 respondents, and demonstrate transparent methodology including polling mode, sample source, and weighting procedures. Scientific sampling methods attempting to achieve representative samples are mandatory, as is the disclosure of poll sponsorship and funding sources. The dataset explicitly excludes non-scientific polls lacking representative sampling, MRP-smoothed data, recontact surveys, DIY polls from nonprofessional sources, polls with leading questions or hypothetical matchups, and subsamples from multi-state polls without geographic verification.

The aggregation phase, finally, involves rating polls by pollster polling quality (ranging from 0.5 to 3.0 stars), with polls with higher historical accuracy, lower consistent partisan biases, and higher transparency of methodology boasting higher ratings. FiveThirtyEight then applies quality adjustments, including house effects corrections for systematic pollster biases, mode effects adjustments for sampling method biases, population adjustments between likely and registered voters, third-party candidate inclusion effects, and partisan poll adjustments.

Several important measurement limitations to FiveThirtyEight's methodology must be acknowledged. These include temporal gaps between polls creating discontinuous measurement of voter sentiment, response rates and participation biases potentially skewing samples, and varying geographic coverage with swing states being overrepresented. Additionally, third-party candidate treatment varies across polls, while house effects and mode effects corrections rely on historical patterns that may not hold true in current contexts.

@@

The aggregated polling data includes support percentages of different presidential candidates in polls with different FiveThirtyEight ratings [@5382] across two elections. Please view [UPDATE APPENDIX] for summary statistics of sub-datasets.

@@

The predictor variables that we ended up using in our final logistic regression model were the poll end dates, transparency score, and sample sizes of the polls, as well as whether or not a poll was sponsored. The distributions of the variables is as follows:

@@

```
\FloatBarrier
The end date indicates the date that a poll ends on. The dates are graphed separately between the 2020 and 2024 cycles for ease of viewing. Notice how there is a disproportionately large uptick in the number of polls that end on the end of a month.

### Sponsors

@@

Has_sponsor is a categorical variable that keeps track of whether the poll is sponsored by a third party other than the one conducting the poll itself. This is distributed roughly 60-40, with the larger portion of polls being independently funded (i.e. no sponsors).

@@

The transparency score is a metric given to a poll/pollster by 538 that measures the transparency of the methodology with which the poll is conducted. This is done through a 10-question yes/no checklist on how much of the methodology is available to the public - note how this is completely separate from the quality of the methodology itself. Each question is graded on a 0/0.5/1 scale, for a combined transparency score that ranges from 0 to 10 [@5383]. Most polls in our dataset miss the mark on one or two criteron, netting a final transparency score of 9 - this is partially due to the data cleaning process removing many relatively worsely conducted polls.

@@

Sample size, finally, is a measure of the number of participants in each poll. Around 1000 participants seems to overwhelmingly be the final survey size that pollsters decide on, with only single-digit numbers of polls (with rating >= 2.5) boasting more than four thousand respondents.

@@

# Appendix {-}
## Pollster methodology overview and evaluation
The Quinnipiac University Poll conducts independent polling in swing states. To analyze their methodology, we look specifically into their October 2024 Pennsylvania polls [@quinnipiac].

Their target population is likely voters aged 18 and older in Pennsylvania [@quinnipiacmethodology]. To reach this population, they use likely voters aged 18 and older with phone numbers (both landline and cell) as their sampling frame, i.e. the frame of possible subjects that they sample observations from. Quinnipiac University employed Random Digit Dialing (RDD) to generate their sample of 2,186 respondents. This dual-frame approach reflects modern communication patterns, with 1,644 cell phone and 542 landline completions. However, using phones as a sampling frame means they cannot reach voters without phone access, introducing potential coverage bias.

Their sampling approach uses stratification by Census division according to area code, meaning that they divide Pennsylvania into geographic regions before using RDD to sample within each region. This strategy ensures even geographic representation but adds complexity to the sampling process [@pollofpolls]. For each selected number, they attempt contact at least three times before marking it as non-responsive. For landline calls, they ask to speak with the household member who has the next birthday, a simple but effective randomization technique. Afterwards, a series of screening questions confirm that the subject is indeed a likely voter, after which the subject's responses are then formally taken as part of the sample.

After collecting responses, Quinnipiac adjusts their data through post-stratification weighting. In this weighting, they compare their sample's demographic composition to known population benchmarks from the Census (like age, gender, education, and race distributions in Pennsylvania) and adjust the weight given to each response to match these benchmarks. For example, if their sample has too few young voters compared to Census data, responses from young voters would be weighted more heavily. While this helps correct for sampling imbalances, it can increase the variance in their estimates if the weights vary substantially [@poststratification].

The survey administration addresses measurement issues through its design. Live interviewers conduct all interviews, enabling question clarification and generating higher response rates compared to automated systems. However, live interviewers may introduce social desirability bias, where respondents might modify their answers to appear more socially acceptable. This becomes particularly relevant in political polling, where respondents might hesitate to express unpopular political views [@politicalpolling].

Several types of bias affect the poll's results. Self-selection bias occurs because certain types of people (typically those more politically engaged or with stronger views) are more likely to agree to participate in the survey. Non-response bias arises when people who respond differ systematically from those who don't - for instance, busier people might be less likely to answer calls, potentially underrepresenting certain occupational groups [@nonresponse]. Coverage bias means some groups (like those without phones) have no chance of being included in the sample.

@@

Overall, Quinnipiac's methodology represents a balanced approach to managing practical constraints and statistical rigor in modern political polling - while some common biases are still likely to skew the poll results off the true support levels for Harris, for example, the poll uses methods such as post-stratification weighting to tradeoff biases at the cost of model variance [@weighting]. Using live interviewers unavoidably introduces social desirability bias, however, and significantly increases poll costs per quota. Modifying the methodology to remove this aspect of the survey would potentially reduce bias and allow for larger samples to be taken, in turn opening up possibilities for cross-validation and the such, which then reduces the effect of increased model variance on the final results.

@@

Our sampling strategy employs both probability and non-probability methods. Probability sampling (60% of budget, i.e. $60k) means every member of our target population has a known, non-zero chance of being selected - this allows us to calculate proper margins of error and make statistical inferences about the population. For this, we use dual-frame random digit dialing (RDD) for phone surveys and address-based sampling (ABS) for mail-to-web recruitment. RDD involves generating random phone numbers within active area codes, while ABS uses the U.S. Postal Service's delivery database as a sampling frame, both proven methods of sampling [@cummings]. The ABS approach helps reach households without reliable phone access. We stratify our sample by geography, demographics, and previous voting patterns to ensure representation across key subgroups - meaning we divide the population into these subgroups and sample from each independently.

For non-probability sampling (40% of budget, i.e. $40k), where respondents' selection probabilities are unknown and not everyone has a chance of being selected, we recruit through multiple online panel vendors and use targeted social media advertising to reach traditionally underrepresented groups. While this approach introduces potential selection bias because participants self-select into the sample, it helps reach younger voters who are less responsive to traditional survey methods [@nonprobabilitysampling]. We implement quota sampling within these non-probability samples to match key demographic targets - for example, stopping collection from certain demographic groups once their quota is filled.

@@

Our weighting approach uses post-stratification to known population benchmarks - this means we adjust the weight given to each response so that our sample matches known population characteristics. For example, if our sample has 30% college graduates but the population has 40%, we would give more weight to responses from college graduates. We include demographics (age, race, education, gender), geographic location, past voting behavior, and party registration in our weighting scheme. We produce daily estimates using a 7-day rolling average, which helps smooth out daily fluctuations while remaining responsive to real changes in voter preferences [@weighting2].

Finally, how ethics are handled is a crucial part of any survey methodology. In this idealised methodology, consent will be asked for at the beginning of the survey, full disclosure of how information is used will be given beforehand and no self-identifiable information will be recorded (so no names, phone numbers, etc.). The $10 incentive is enough to hopefully make it wortile for participants' time, but also not ideally not significant enough of an incentive to make individuals suppress otherwise deal-breaking concerns with the survey purely for the sake of the incentive.
